Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-18 paper/uist_2016/paper.tex
moving around/deleting pics

\subsubsection{Hyperlapse Creation} 
Each video recollection created by \textit{Rewind} is composed of two hundred Google Street View image sequences of the chosen route being stitched together using StreetViewSequence \cite{streetviewsequence}. Each incoming Google Street View image has been retrieved with the same dimensions (640 px by 640 px) with similar spatial orientation (FOV, pitch and heading values).

@@

\begin{figure}
   \centering
     \includegraphics[width=1\linewidth]{Rewind-seasons2}
     \caption{Plantation is classified using HSV color space, and the HSV values were adjusted to reflect seasonal changes}
     \label{fig:season}
\end{figure}

\begin{figure}
   \centering
     \includegraphics[width=1\linewidth]{Rewind-weather}
     \caption{Meterological attributes are depicted using JavaScript canvas painting and animation}
     \label{fig:weather}
\end{figure}

>>>>

\subsubsection{Hyperlapse Creation} 
\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{Rewind-seasons2}
	\caption{Plantation is classified using HSV color space, and the HSV values were adjusted to reflect seasonal changes}
	\label{fig:season}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{Rewind-weather}
	\caption{Meterological attributes are depicted using JavaScript canvas painting and animation}
	\label{fig:weather}
\end{figure*}

Each video recollection created by \textit{Rewind} is composed of two hundred Google Street View image sequences of the chosen route being stitched together using StreetViewSequence \cite{streetviewsequence}. Each incoming Google Street View image has been retrieved with the same dimensions (640 px by 640 px) with similar spatial orientation (FOV, pitch and heading values).

@@
